DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-08-16 ase2017/paper.tex
fixed typos in section V
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\renewcommand{\baselinestretch}{0.99}
\newcommand\tool{{DSSynth Toolbox}\xspace}
\newcommand{\fwl}[1]{\mathcal{FWL}[#1]}

@@

For all evaluated benchmarks, the signal input range related to the control
system is between $-1$ and $1$.  The implementation features used for
digital controller are: $8$~bits for the integer part (including the sign
bit) and $8$~bits for the fractional part.  We have run the \tool using
CEGIS with multi-staged verification (cf.~Section~\ref{sec:CEGIS}).  All
experiments with \tool v$1$.$0$.$0$ were conducted on an otherwise idle
Intel Core i$7-2600$ $3.40$ GHz processor, with $24$ GB of RAM, running
Ubuntu $64$-bit.

@@

The \tool can automatically synthesize stable and safe digital controllers
for intricate dynamic physical plants, represented in MATLAB either as a
transfer function or a state-space equation.  The \tool is the first fully
automated synthesis tool that is algorithmically and numerically sound,
considering various error sources in the implementation of the digital
control algorithm and in the computational modeling of plant
dynamics~\cite{abate2017, abatecav2017}.
%
The \tool presents a practical application of CEGIS-based program synthesis.
Tractable program synthesis in control engineering encourages the application
of this technique in other fields such as program repair or superoptimisation.
%
Additionally, given the current literature in controller synthesis, there is
no other MATLAB toolbox for synthesizing stable and safe digital controllers
for physical plants that considers all aspects of their digital
implementation.
%
As future work, the \tool will perform synthesis considering additional
requirements (e.g., performance) and will be combined with the
DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to
verify/validate further controller properties.
We will also pursue the application of CEGIS to software
engineering problems.

>>>>

\renewcommand{\baselinestretch}{0.986}
\newcommand\tool{{DSSynth Toolbox}\xspace}
\newcommand{\fwl}[1]{\mathcal{FWL}[#1]}

@@

For all evaluated benchmarks, the signal input range related to the control
system is between $-1$ and $1$.  The implementation features used for
digital controller are: $8$~bits for the integer part (including the sign
bit) and $8$~bits for the fractional part.  We~have run the \tool using
CEGIS with multi-staged verification (cf.~Section~\ref{sec:CEGIS}).  All
experiments with \tool v$1$.$0$.$0$ were conducted on an otherwise idle
Intel Core i$7-2600$ $3.40$ GHz processor, with $24$ GB of RAM, running
Ubuntu $64$-bit.

@@

The \tool can automatically synthesize stable and safe digital controllers
for intricate dynamic physical plants, represented in MATLAB either as a
transfer function or a state-space equation.  The \tool is the first fully
automated synthesis tool that is algorithmically and numerically sound,
considering various error sources in the implementation of the digital
control algorithm and in the computational modeling of plant
dynamics~\cite{abate2017, abatecav2017}.
%
The \tool presents a practical application of CEGIS-based program synthesis.
Our results in control engineering encourages the application
of this technique in other fields such as program repair or superoptimisation.
%
Additionally, given the current literature in controller synthesis, there is
no other MATLAB toolbox for synthesizing stable and safe digital controllers
for physical plants that considers all aspects of their digital
implementation.
%
As future work, the \tool will perform synthesis considering performance
requirements and will be combined with the
DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to
verify/validate other controller properties.
We will also pursue the application of CEGIS to further software
engineering problems.
